Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-07-03 paper/paper.tex
cite prior work on strf visualization

Observe that the equation above is a limit case of $\mathbf{S_2}$ (Equation \ref{eq:S2}) in which the constants $T$ and $F$ tend towards infinity.
As a result, $\mathbf{V}\boldsymbol{x}$ depends solely upon scale $\alpha$ and rate $\beta$.
In the scientific literature on spectrotemporal receptive fields (STRF), the matrix $\mathbf{V}\boldsymbol{x}$ is called ``cortical output collapsed on the rate-scale axes'' \cite{elhilali2002speechcomm}.

Previous publications on STRF have focused on the visualization of synthetic stimuli and speech. % refs?
%Although one publication has turned to the visualization of isolated musical notes, the scope of discussion on the effect of technique is

>>>>

Observe that the equation above is a limit case of $\mathbf{S_2}$ (Equation \ref{eq:S2}) in which the constants $T$ and $F$ tend towards infinity.
As a result, $\mathbf{V}\boldsymbol{x}$ depends solely upon scale $\alpha$ and rate $\beta$.
In the scientific literature on spectrotemporal receptive fields (STRF), the matrix $\mathbf{V}\boldsymbol{x}$ is called ``cortical output collapsed on the rate-scale axes'' \cite{elhilali2003speechcomm}.

Previous publications have demonstrated the interest of visualizing the slice $\mathbf{V}\boldsymbol{x}$ in the case of speech \cite{bellur2015ciss}, lung sounds \cite{emmanouilidou2012embs}, and music \cite{patil2012ploscompbiol}.
%Although one publication has turned to the visualization of isolated musical notes, the scope of discussion on the effect of technique is
